---
title: "Single Document"
author: "Yingting Zhang"
date: "2023-09-20"
output: github_document
---

# Problem 1

* load the moderndive library
```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```

  * the variables in this dataset, including names / values of important variables
  * the size of the dataset (using nrow and ncol)
  
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```

  * the mean temperature
```{r}
mean(early_january_weather$temp)
```

Short Description:
According to the dataset, we can see that there are 15
variables, including origin, year, month, day, hour, temp, dewp, humid, wind_dir,
wind_speed, wind_gust, precip, pressure, visib, and time_hour. The size of 
dataset includes 358 rows and 15 columns. The mean of temperature is `r mean(early_january_weather$temp)`.

* make a scatterplot of temp (y) vs time_hour (x):
```{r}
library(tidyverse)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```


* Describe patterns that are apparent in this plot:
As time goes on, the temperature zigzag increased and at the highest peak, 
after the date on Jan 14th, it suddenly dropped. As the part of humidity data, 
the data between 40-60 make up a large part during the range of time_hour.

* Export scatterplot to your project directory 
```{r}
ggsave("scatter_plot.pdf",height = 4, width = 4)
```

# Problem 2

* Create a data frame comprised of:

  * a random sample of size 10 from a standard Normal distribution
  * a logical vector indicating whether elements of the sample are greater than 0
  * a character vector of length 10
  * a factor vector of length 10, with 3 different factor “levels”

```{r}
q2=tibble(
  norm_samp = rnorm(10),
  log_samp = norm_samp > 0,
  character_vec = c("one","two","three","four","five","six","seven",
                     "eight","nine","ten"),
  factor_vec = factor(c("LevelA", "LevelB", "LevelC","LevelA", "LevelB", "LevelC",
                        "LevelA", "LevelB", "LevelC","LevelA"))
)
```

* take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
mean(pull(q2,norm_samp))
mean(pull(q2,log_samp))
mean(pull(q2,character_vec))
mean(pull(q2,factor_vec))
```
According to the results, we can see that the mean of a random sample of size 10
is `r mean(pull(q2,norm_samp))`, with the logical vector 0.5, however, the last two variable which
are character vector and factor vector don't work because they are neither 
numeric nor logical returning.

* Using as.numeric function to the logical, character, and factor variables
```{r eval=FALSE}
as.numeric(pull(q2,log_samp))
as.numeric(pull(q2,character_vec))
as.numeric(pull(q2,factor_vec))
```

According to the results, the result of factor vector shows the values of 1,2,3 
corresponding to the levels of factor; the result of logical vector convert TRUE
as 1 and FALSE as 0; it doesn't work for character vector as there is no numeric
value in it. 

* Explain why or why not when calculate their means?
  * Logical vector: a logical vector can be converted into numeric value (TRUE=1,
  FALSE=0). In this case, this can calculate the mean
  * Character vector: a character vector with character values
  cannot convert into numeric values, which calculate the mean
  * Factor vector: although we can use "as.numeric" function" to convert factor
  levels into numeric format, the data are not truly numeric values, presenting
  levels numerically. In this case, this cannot calculate the mean
  
